---
title: "Combining Open GWAS and EBI GWAS catalog information"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Combining Open GWAS and EBI GWAS catalog information}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

```{r setup,echo=FALSE,results="hide"}
suppressMessages({
suppressPackageStartupMessages({
library(gwaslake)
library(dplyr)
library(DT)
})
})
```

# Aim

Our aim here is to improve curation of Open GWAS records by coupling
to the EBI GWAS catalog.

Here are previews of `gwinf` (Open GWAS) and `ebi` (EBI catalog)
resources.
```{r lkinfo, cache=TRUE}
library(ieugwasr) # from github mrcieu
library(gwascat)
gwinf = gwasinfo()
gwinf
ebi = get_cached_gwascat()
ebi
```

# Data filtering and merging

## Confine `gwinf` to records with accession numbers

We'll likely only gain information for records with GCST (study accession)
tags.
```{r filter1}
gwinf = gwinf[grep("GCST", gwinf$id),]
dim(gwinf)
gwinf$acc = gsub("ebi-..", "", gwinf$id)
```

## Filter the EBI catalog to studies

The EBI catalog has locus-specific records; we are interested in
studies.

```{r reduce}
ebi = ebi[-which(duplicated(ebi$`STUDY ACCESSION`)),]
```

## Merge and inspect

```{r merge}
nn = inner_join(mutate(ebi, acc=`STUDY ACCESSION`), gwinf, by="acc")
dim(nn)
library(DT)
datatable(nn)
```
